Despite its scale and grounding in real-world data, this work has several important limitations that constrain the interpretation and generalizability of our results.

\textbf{Evaluation scope.} RetailBench focuses on a single-store supermarket setting and does not capture multi-store coordination, competitive markets, or strategic interactions among multiple autonomous agents. Although the environment incorporates stochastic demand, news dynamics, and supply-chain delays, it remains a simulation based on historical data and simplified economic assumptions, which may not fully reflect the complexities of real-world retail systems. External validity beyond this simulated setting remains to be established.

\textbf{Statistical rigor.} Due to computational constraints, our current evaluation uses a limited number of experimental runs (three runs per model in most settings). The reported performance differences should be interpreted as preliminary observations rather than statistically significant conclusions. Rank orderings may be sensitive to random seed selection, and effect sizes may vary with additional repetitions. We plan to extend our evaluation with paired-seed experimental designs and formal significance testing in future work.

\textbf{Reproducibility and comparability.} Our evaluation uses multiple closed-source model variants with potentially different API versions, token budgets, and inference configurations. Mixed model variants (``lower-cost variants when available'') and unclear budget parity across frameworks introduce confounding factors that may affect comparability of results. API version drift and non-deterministic inference in closed models pose additional reproducibility risks.

\textbf{Causal claims.} Our comparison of agent frameworks demonstrates associations between framework design and performance metrics, but does not establish causal relationships. Performance differences may be attributable to factors including token budget, prompt engineering, or model-specific behaviors rather than framework architecture alone. Controlled ablation studies are needed to isolate the causal impact of individual framework components.

\textbf{Baseline strength.} Our current baselines include rule-based heuristics and agent framework variants, but do not include strong classical operations research methods such as $(s,S)$ inventory policies or newsvendor-based ordering strategies. The relative performance of LLM-based agents compared to these well-established methods remains unknown and is an important direction for future investigation.

\textbf{Learning and adaptation.} Our evaluation focuses on prompting-based LLM agents without parameter updates or inter-episode learning. Stronger performance may be achievable through reinforcement learning, fine-tuning, or hybrid neuro-symbolic approaches. Our findings should be interpreted as characterizing zero-shot prompting performance rather than the full potential of learned agent systems.

\textbf{Failure mode analysis.} While we identify recurring patterns such as hallucinations and economically irrational actions, we do not propose explicit algorithmic mechanisms to enforce economic rationality or factual grounding during execution. Addressing these failure modes through constraint-aware action control remains an important open problem.

\textbf{Domain specificity.} Our findings are specific to the retail operations domain and the RetailBench environment. Transferability to other decision-making domains---such as manufacturing, logistics, or financial trading---requires empirical validation and should not be assumed without evidence.